### 2009-10-30 doc/tech_doc/chelonia/arc-storage-documentation.tex
client.xml removed

The credentials of the user and the URL of the Bartender must be configured either with an XML file located at \verb!~/.arc/client.xml! or with environment variables. (The environment variables overwrite the values from the XML file.)

An example of user credentials and Bartender configuration in the \verb!~/.arc/client.xml! file:

\begin{verbatim}
    <ArcConfig>
      <ProxyPath>/Users/zsombor/Development/arc/proxy</ProxyPath>
      <CACertificatesDir>/Users/zsombor/Development/arc/certs/CA</CACertificatesDir>
      <BartenderURL>https://localhost:60000/Bartender</BartenderURL>
    </ArcConfig>
\end{verbatim}

@@

As for the \verb!chelonia! the credentials of the user and the URL of the Bartender can be configured either with an XML file located at \verb!~/.arc/client.xml! or with environment variables. See Section \ref{sub:prototype_cli_tool} for more details.

@@

As with the \verb!chelonia! command the credentials of the user and the URL of the Bartender can be configured with an XML file located at \verb!~/.arc/client.xml!. When the ARC DMC is initiated, it will create an instance of \verb!DataPointARC! which provides functionality for listing collections and file IO. When downloading/uploading files from/to the storage system, the data point will use the provided Bartender URL to acquire a TURL from a Bartender. This TURL will be given to a \verb!DataTransfer! handle. Calling the constructor of the DataHandle class with a URL will trigger the iGetDataPoint class of all registered DMC's to be called until a non-NULL pointer is returned. This means that as long as there exists a data point plugin for the protocol of the returned TURL, the transfer will proceed.

>>>>

The credentials of the user and the URL of the Bartender must be
configured either with an ini configuration file located at \verb!~/.arc/client.conf! or with environment variables. (The environment variables overwrite the values from the ini file.)

An example of user credentials and Bartender configuration in the \verb!~/.arc/client.ini! file:

\begin{verbatim}
[common]
proxypath=/Users/zsombor/Development/arc/proxy
cacertificatesdirectory=/Users/zsombor/Development/arc/certs/CA
bartender=https://localhost:60000/Bartender
\end{verbatim}

@@

As for the \verb!chelonia! the credentials of the user and the URL of
the Bartender can be configured either with an ini configuration file located at \verb!~/.arc/client.conf! or with environment variables. See Section \ref{sub:prototype_cli_tool} for more details.

@@

As with the \verb!chelonia! command the credentials of the user and
the URL of the Bartender can be configured with an ini configuration file located at \verb!~/.arc/client.conf!. When the ARC DMC is initiated, it will create an instance of \verb!DataPointARC! which provides functionality for listing collections and file IO. When downloading/uploading files from/to the storage system, the data point will use the provided Bartender URL to acquire a TURL from a Bartender. This TURL will be given to a \verb!DataTransfer! handle. Calling the constructor of the DataHandle class with a URL will trigger the iGetDataPoint class of all registered DMC's to be called until a non-NULL pointer is returned. This means that as long as there exists a data point plugin for the protocol of the returned TURL, the transfer will proceed.
